Order-Adaptive Regularisation for Variational Optic Flow:\\Global, Local and in Between

### 2018-07-17 seminar_vof/paper/paper.tex
1st order reg intuition

\subsection{Dataterm}
The employed data term in the variational model uses a combination of brightness and gradient constancy assumption.
\begin{flalign}
\label{eq:dataterm}
D(\flow) &= \int_\Omega \charbonnier(p_{\text{brght}}(\flow)) + \gamma*\charbonnier(p_{\text{grad}}(\flow))\;d\x &&
\\\label{eq:brightnessconstancy}
p_{\text{brght}}(\flow) &= (\;I_1(\x+\flow(\x))-I_0(\x)\;)^2 &&
\\\label{eq:gradientconstancy}
p_{\text{grad}}(\flow) &= ||\;\nabla I_1(\x+\flow(\x))-\nabla I_0(\x)\;||_2^2 &&
\end{flalign}
In this setup, $p_{\text{brght}}$ is the penalizer for the brightness constancy assumption and $p_{\text{grad}}$ is the penalizer for the gradient constancy assumption which can be understood as a check for
edges being mapped correctly.
The parameter $\gamma$ is used to weight the terms against each other.
As can be seen $p_{\text{brght}}$ and $p_{\text{grad}}$ are quadratic penalizers, and are thus sensitive to outliers.
To remove the strong influence of outliers on the minimization, the subquadratic charbonnier penalizer \cite{charbonnier} $\charbonnier$ is used to 
robustify both constancy assumptions.
\begin{flalign}\label{eq:charbonnier}
\charbonnier(s^2) &= 2\epsilon^2\sqrt{1+s^2/\epsilon^2} &&
\end{flalign}
Note that the charbonnier penalizer is a function of a squared argument so that an arbitrary quadratically penalized assumption can be plugged in.
When plotting the function with respect to $s$ instead of $s^2$ its behaviour becomes clearer, as shown in \cref{fig:penalizers}.
For values close to zero, the function penalizes quadratically and approaches linear behaviour in the limit $s\to\pm\infty$, resulting in outliers being less fatal.

\subsection{Regulalarisation}
As said in \cref{sec:motivation} the variational model is able to adaptively choose regularization order. 
Therfore the regularisation term is a combination of a first and a second order part.
Lets first have a look at the first oreder regularizer $\Rfirst$. 
\begin{flalign}
\Rfirst(\flow) &= \int_\Omega S_1(\flow)\;d\x&&
\\
S_1(\flow) = \sum_{l=1}^2
\end{flalign}

\begin{figure}[htb]
\centering
\begin{subfigure}{0.49\linewidth}
\centering
\includegraphics[width=\linewidth]{images/charbonnier.eps}
\end{subfigure}
\begin{subfigure}{0.49\linewidth}
\centering
\includegraphics[width=\linewidth]{images/peronamalik.eps}
\end{subfigure}
\caption{
Graphs show penalizer functions and their asymptotic equivalents as dashed lines.\\
Left is charbonnier \cref{eq:charbonnier} with $\epsilon=1$ and asymptotic equivalents $\lim_{s\to 0}\charbonnier(s^2)=s^2+2$ and $\lim_{s\to\infty}\charbonnier(s^2)=2s$.\\
Right is Perona Malik \cref{eq:peronamalik} with $\epsilon=1$ and asymptotic equivalents $\lim_{s\to 0}\peronamalik(s^2)=s^2$ and $\lim_{s\to\infty}\peronamalik(s^2)=2\ln(s)$.
}
\label{fig:penalizers}
\end{figure}

>>>>

\subsection{Dataterm}\label{sec:dataterm}
The employed data term in the variational model uses a combination of brightness and gradient constancy assumption.
\begin{flalign}
\label{eq:dataterm}
D(\flow) &= \int_\Omega \charbonnier(p_{\text{brght}}(\flow)) + \gamma*\charbonnier(p_{\text{grad}}(\flow))\;d\x &&
\\\label{eq:brightnessconstancy}
p_{\text{brght}}(\flow) &= (\;I_1(\x+\flow(\x))-I_0(\x)\;)^2 &&
\\\label{eq:gradientconstancy}
p_{\text{grad}}(\flow) &= ||\;\nabla I_1(\x+\flow(\x))-\nabla I_0(\x)\;||_2^2 &&
\end{flalign}
In this setup, $p_{\text{brght}}$ is the penalizer for the brightness constancy assumption and $p_{\text{grad}}$ is the penalizer for the gradient constancy assumption which can be understood as a check for
edges being mapped correctly.
The parameter $\gamma$ is used to weight the terms against each other.
As can be seen $p_{\text{brght}}$ and $p_{\text{grad}}$ are quadratic penalizers, and are thus sensitive to outliers.
To remove the strong influence of outliers on the minimization, the subquadratic charbonnier penalizer \cite{charbonnier} $\charbonnier$ is used to 
robustify both constancy assumptions.
\begin{flalign}\label{eq:charbonnier}
\charbonnier(s^2) &= 2\epsilon^2\sqrt{1+s^2/\epsilon^2} &&
\end{flalign}
Note that the charbonnier penalizer is a function of a squared argument so that an arbitrary quadratically penalized assumption can be plugged in.
When plotting the function with respect to $s$ instead of $s^2$ its behaviour becomes clearer, as shown in \cref{fig:penalizers}.
For values close to zero, the function penalizes quadratically and approaches linear behaviour in the limit $s\to\pm\infty$, resulting in outliers being less fatal.

\subsection{Regulalarisation}
As said in \cref{sec:motivation} the variational model is able to adaptively choose regularization order. 
Therfore the regularisation term is a combination of a first and a second order part.
Lets first have a look at the first oreder regularizer $\Rfirst$. 
\begin{flalign}
\Rfirst(\flow) &= \int_\Omega S_1(\flow)\;d\x&&
\\\label{eq:S1}
S_1(\flow) &= \peronamalik\Big((\ev_1\T\nabla u)^2+(\ev_1\T\nabla v)^2\Big)
+ \charbonnier\Big((\ev_2\T\nabla u)^2+(\ev_2\T\nabla v)^2\Big)&&
\end{flalign} 
This is the anisotropic complementary regulariser by Zimmer~et~al.~\cite{opticflowinharmony} which makes use of the eigenvectors of the regularisation tensor \cite{opticflowinharmony}.
The regularization tensor is a generalization of the structure tensor \cite{maxanisotropy} for arbitrary image features.
In short, it summarizes gradient information within a neighborhood of a pixel.
The eigenvector $\ev_1$ points in the direction of steepest change (i.e. over an edge) while $\ev_2$ is orthogonal to $\ev_1$ (i.e. points along an edge).

Lets postpone the discussion of the regularization tensor for a second and get some intuition on the way $S_1$ works.
As can be seen from \cref{eq:S1}, the term uses two penalizer functions, the Charbonnier penalizer which was introduced in \cref{sec:dataterm} in \cref{eq:charbonnier} and the Perona~Malik penalizer $\peronamalik$.
\begin{flalign}\label{eq:peronamalik}
\peronamalik(s^2) &= \epsilon^2\ln(1+s^2/\epsilon^2)&&
\end{flalign}
As arguments to the penalizer functions, projections of the flow gradients onto the eigenvectors are used.
These projections are minimal if the flow gradient vanishes as in standard first order smoothness terms.
Special about this term are the different penalizations of projections on the first and second eigenvector respectively.
The graphs of the two penalizer functions are shown in \cref{fig:penalizers}, where it can be seen that values close
to zero are penalized quadratically, values further away are penalized subquadratically in both functions.
In the limit however, the Perona-Malik penalizer takes on smaller values than the charbonnier penalizer.
This has the effect of flow changes in direction of the first eigenvector to be less costly than in direction of the second eigenvector.
From the perspective of image features and the regularization tensor this is like getting a \enquote{discount} on flow change over an edge.
\begin{figure}[htb]
\centering
\begin{subfigure}{0.49\linewidth}
\centering
\includegraphics[width=\linewidth]{images/charbonnier.eps}
\end{subfigure}
\begin{subfigure}{0.49\linewidth}
\centering
\includegraphics[width=\linewidth]{images/peronamalik.eps}
\end{subfigure}
\caption{
Graphs show penalizer functions and their asymptotic equivalents as dashed lines.\\
Left is charbonnier \cref{eq:charbonnier} with $\epsilon=1$ and asymptotic equivalents $\lim_{s\to 0}\charbonnier(s^2)=s^2+2$ and $\lim_{s\to\infty}\charbonnier(s^2)=2s$.\\
Right is Perona Malik \cref{eq:peronamalik} with $\epsilon=1$ and asymptotic equivalents $\lim_{s\to 0}\peronamalik(s^2)=s^2$ and $\lim_{s\to\infty}\peronamalik(s^2)=2\ln(s)$.
}
\label{fig:penalizers}
\end{figure}

To continue the discussion of the regularization tensor, lets state its definition first.
\begin{flalign}
S_\Phi(\x) = \bigintsss \omega(\tau)\Mat{\Phi_x(\x-\tau)^2 && \Phi_x(\x-\tau)\Phi_y(\x-\tau)\\\Phi_x(\x-\tau)\Phi_y(\x-\tau) && \Phi_y(\x-\tau)^2} \;d\tau
\end{flalign}
